???A quantitative framework for investigating the reliability of network construction

### 2017-09-22 manuscript/CI_interactions.tex
added a preliminary bibliography and a couple more refs

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}. Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{}). Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described \emph{Salix} galler-parasitoid system (doi: 10.1073/pnas.1513633113). Note that this study used several genotypes of \emph{S. hookeriana} rather than different \emph{Salix} species. We estimated frequencies of  \emph{S. hookeriana} genotype-galler and galler-parasitoid interactions [[host-parasitoid still to-do]] based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).

@@

      For species where no co-occurances were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Balbour2016} is:
      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541. [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset. This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Balbour2016}.}
        \label{interval_table}
        \begin{tabular}{l | c c}
        N & Lower bound & Upper bound \\
        \hline
        0   & 0.157 & 0.901 \\
        2   & 0.099 & 0.743 \\
        4   & 0.072 & 0.621 \\
        6   & 0.057 & 0.530 \\
        8   & 0.047 & 0.462 \\
        10 & 0.040 & 0.408 \\
        14 & 0.031 & 0.331 \\
        20 & 0.023 & 0.258 \\
        30 & 0.016 & 0.188 \\
        40 & 0.012 & 0.148 \\
        50 & 0.010 & 0.122 \\
        \hline
        374 & 0.001 & 0.018 \\
        \hline
        \end{tabular}
        \end{table}

@@

    \bibliographystyle{ecollett} 
    \bibliography{manual_abbrev} % Abbreviate journal titles.

>>>>

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. The removal of a species from a site will obviously also remove its interactions. Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}. Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}). Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.

@@

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described \emph{Salix} galler-parasitoid system~\citep{Barbour2016,Barbour2016Dryad}. Note that this study used several genotypes of \emph{S. hookeriana} rather than different \emph{Salix} species. We estimated frequencies of  \emph{S. hookeriana} genotype-galler and galler-parasitoid interactions [[host-parasitoid still to-do]] based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).

@@

      For species where no co-occurances were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541. [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset. This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
        \label{interval_table}
        \begin{tabular}{l | c c}
        N & Lower bound & Upper bound \\
        \hline
        0   & 0.157 & 0.901 \\
        2   & 0.099 & 0.743 \\
        4   & 0.072 & 0.621 \\
        6   & 0.057 & 0.530 \\
        8   & 0.047 & 0.462 \\
        10 & 0.040 & 0.408 \\
        14 & 0.031 & 0.331 \\
        20 & 0.023 & 0.258 \\
        30 & 0.016 & 0.188 \\
        40 & 0.012 & 0.148 \\
        50 & 0.010 & 0.122 \\
        \hline
        374 & 0.001 & 0.018 \\
        \hline
        \end{tabular}
        \end{table}

@@

    \bibliographystyle{ecollett} 
    \bibliography{MyCollection} % Abbreviate journal titles.
